\documentclass[11pt]{article} % set main text size

\usepackage[a4paper,
top=0.4in,
bottom=0.4in,
left=0.5in,
right=0.5in]{geometry}

\usepackage{XCharter}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{titlesec}
\usepackage{xcolor}
\usepackage{fontawesome}

\raggedright
\pagestyle{empty}

\input{glyphtounicode}
\pdfgentounicode=1

\titleformat{\section}{\bfseries\large}{}{0pt}{}[\vspace{1pt}\titlerule\vspace{-6.5pt}]

\renewcommand\labelitemi{$\vcenter{\hbox{\small$\bullet$}}$}
\setlist[itemize]{itemsep=-2pt, leftmargin=12pt}

\begin{document}

% Name
\centerline{\Huge Harshit Dudhani}
\vspace{3pt}

% Contact Info
\centerline{
\href{mailto:harshitdudhani072@gmail.com}{\underline{harshitdudhani072@gmail.com}} |
\href{https://github.com/harshitdudhani}{\underline{GitHub}} |
\href{https://www.linkedin.com/in/harshit-dudhani-777061297/}{\underline{LinkedIn}}
}
\vspace{-15pt}

% Education
\section*{Education}
\textbf{Indian Institute of Information Technology} \hfill {Pune, MH}\\
\textit{Bachelor of Technology in Computer Science} \hfill \textbf{CGPA:} 7.93 \\
\hfill \textit{October 2022 - July 2026 (expected)}

\vspace{2pt}
\textbf{Class XII (CBSE)} \hfill \textbf{Percentage:} 96\% \\
\textit{Sanskar International Academy} \hfill \textit{March 2022}

\vspace{-12pt}

% Projects
\section*{Projects}

\textbf{QuizNest – A Quiz Application} | \emph{Java, Swing, File I/O, Networking}
\hfill \textbf{\href{https://github.com/harshitdudhani/QuizNest}{\color{blue}\faGithub}}
\vspace{-3pt}
\begin{itemize}
\item Quiz platform supporting both online and offline formats.
\item Features: Solo Quiz, API Quiz, and 1v1 Quiz with client–server networking.
\item Built with Java Swing, file handling, and socket programming.
\item Integrated a leaderboard system for competitive gameplay and progress tracking.
\end{itemize}
\vspace{-4pt}

\textbf{OptiRead – OCR Based Text Extraction Software} | \emph{Python, OCR, NumPy, Matplotlib, OpenCV}
\hfill \textbf{\href{https://github.com/harshitdudhani/OptiRead.git}{\color{blue}\faGithub}}
\vspace{-3pt}
\begin{itemize}
\item Developed a software that extracts text from input images using OCR techniques.
\item Generates a \texttt{.txt} file containing the extracted text for easy access.
\item Provides a confidence score of \textbf{0.9+} to ensure reliable recognition.
\item Utilized NumPy, Matplotlib, and OpenCV (\texttt{cv2}) for preprocessing and visualization.
\end{itemize}
\vspace{-4pt}

\textbf{Digital Elevator Control with Adaptive Scheduling} | \emph{Verilog, Digital Design, FSM}
\vspace{-3pt}
\begin{itemize}
\item Designed a digital elevator controller using \textbf{Verilog HDL} with adaptive scheduling logic.
\item Implemented \textbf{finite state machines (FSMs)} to manage elevator movement, floor requests, and door control.
\item Optimized request handling by prioritizing direction-based and nearest-floor scheduling.
\item Simulated and verified functionality using testbenches to ensure correctness and reliability.
\end{itemize}

\vspace{-18pt}

% Skills
\section*{Skills}
\begin{itemize}
\item \textbf{Core Programming:} C, C++, Java, Python, JavaScript, Bash, SQL, HTML, CSS, Verilog.
\item \textbf{Frameworks and Libraries:} React, Tailwind CSS, Vite, Flutter, OCR.
\item \textbf{Databases:} PostgreSQL, MongoDB, MySQL.
\item \textbf{Design and Tools:} Git, GitHub, Linux utilities, Figma, Android Studio, VS Code, IntelliJ IDEA.
\end{itemize}

\vspace{-18pt}

% Achievements
\section*{Achievements}
\begin{itemize}
\item Winner in Rope Climber Competition at \textbf{IIT Roorkee Tech Fest – Cognizance}.
\item Winner in Robo Race Competition at \textbf{BVP Tech Fest}.
\end{itemize}

\vspace{-18pt}

% Position of Responsibility
\section*{Position of Responsibility}

\textbf{Vice President,} \href{https://www.iiitp.ac.in/page/rofies}{\underline{R.O.F.I.E.S - Robotics Club}} — IIIT Pune
\hfill \textit{September 2025 - Present}
\vspace{-5pt}
\begin{itemize}
\item Directed club operations and strategic planning for a team of \textbf{20+ members}.
\item Organized \textbf{5+ major events}, including inter-college robotics competitions and technical workshops.
\item Mentored project leads and established a new member onboarding program.
\end{itemize}

\textbf{PR Head,} Quantnum – Maths Club, IIIT Pune
\hfill \textit{April 2025 - Present}
\vspace{-5pt}
\begin{itemize}
\item Managed outreach, publicity, and event promotion strategies for the Maths Club.
\item Coordinated with external partners to increase participation in club events.
\end{itemize}

\end{document}
